\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\renewcommand*\familydefault{\sfdefault} 
\usepackage{ragged2e}
\usepackage{graphicx}
\author{Dominguez Diaz Alma Juanita}
\title{Design patterns for mobile apps}
\begin{document}
\maketitle
\section{What are design patterns for mobile apps?}
\justify Design patterns are reusable solutions to common software development problems. They have had a significant impact on software development, including mobile app development. The implementation of mobile apps has established some proven models and standards to overcome the challenges and limitations of mobile app development. 
Some common design patterns for mobile apps include:

\subsection{Navigation Patterns:}
\begin{itemize}
\item Tab Bar: Allows users to navigate between different sections or features using tabs placed at the bottom of the screen.

\item Drawer Menu: Utilizes a side panel that can be swiped in to reveal navigation options.

\item Bottom Navigation: Like tab bars but allows for more options and can contain both icons and text.
\end{itemize}

\subsection{Input and Feedback Patterns:}

\begin{itemize}
\item Form Patterns: Standardized ways to display and gather information in forms, including input fields, checkboxes and radio buttons.

\item Feedback Patterns: Notifications, alerts, and confirmation dialogs to provide feedback to users based on their actions.
\end{itemize}

\subsection{ Content Presentation Patterns:}
\begin{itemize}
\item List View: Displaying content in a scrollable list, often used for displaying feeds, messages, or other types of content.
\item Grid View: Displaying content in a grid layout, commonly used for galleries or collections of items.
\end{itemize}

\subsection{Search and Filter Patterns:}
\begin{itemize}
\item Search Bar: Allows users to search for specific content within the app.
\item Filtering Options: Enables users to refine content based on specific criteria or categories.
\end{itemize}

\subsection{Onboarding Patterns:}
\begin{itemize}
\item Tutorials and Walkthroughs: Guides users through the app's features and functionalities.
\item Progressive Onboarding: Introduces new features gradually as users interact with the app.
\end{itemize}

\subsection{Gesture Patterns:}
\begin{itemize}
\item Swipe: Used for navigating between pages or items.
\item Pinch and Zoom: Used for scaling or zooming in on content, especially in image-intensive apps.
\end{itemize}

\subsection{ Action Patterns:}
\begin{itemize}
\item Floating Action Button (FAB): A prominent button used to trigger the app's primary action.
\item Contextual Actions: Actions that appear based on user interactions or selections within the app.
\end{itemize}

\subsection{Loading Patterns:}
\begin{itemize}
\item Skeleton Screens: Placeholder UI elements that show the app structure while content is loading.
\item Progress Indicators: Show the progress of an action, such as downloading or uploading data.
\end{itemize}
\end{document}